### 2016-03-12 experiments.tex
Alex ready to ship

 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs. If each failure was only repaired by one mutant, MUSEUM and {\bf Repair} would both rank that mutant maximally, and we speculate it would usually be faulty.  But such cases are rare:  for SpiderMonkey the mean/median number of mutants repairing each failure were 90.8 and 78, respectively, and for GCC the mean and median were 54 and 43.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs.  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  {\bf Repair} can still distinguish such mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.

>>>>

 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs. If each failure was only repaired by one mutant, MUSEUM and {\bf Repair} would both rank that mutant maximally, and we speculate it would usually be faulty.  But such cases are rare:  for SpiderMonkey the mean/median number of mutants repairing each failure were 90.8 and 78, respectively, and for GCC the mean and median were 54 and 43.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.

{\bf Repair} can distinguish such mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.
